Example case study in GMSE

### 2020-05-24 notebook/ms/SI3.Rmd
Minor edit to the vignete and documentat

|  public_land    |  0      | Proportion of land that is public (un-owned by users) if land_ownership = TRUE                   |

@@

The code below calls `gmse` using the empirically derived parameters for Taiga Bean Geese described above. We also set `manager_budget = 10000` and `user_budget = 10000`. Further, we consider the case of a region in which farmland makes up 60% of all land, with 40% of land being 'public' (`public_land = 0.4`; which might be interpreted as any land in which stakeholders are not, or cannot be, invested in goose presence), and divide the farmland amongst 80 individual farmers (`stakeholders = 80`; `land_ownership = TRUE`). Landscape size is set to default 100 by 100 cells, so each farmer effectively owns 75 cells, which might be interpreted as hectares of land (for instructions on how to more precisely control landscape ownership, see the [advanced GMSE options](SI4.pdf) using `gmse_apply`). Because we need both density-dependent (`res_death_K = 93870`) and density-independent (`remove_pr = 0.122`) sources of mortality, we set `res_death_type = 3`. We assume that a single goose decreases agricultural production on a cell by 2% per time step (`res_consume = 0.02`). We further assume that the population is very well-monitored, with observers counting goose numbers on each cell of the landscape in every timestep (`observe_type = 3`) with the ability to observe one landscape cell in every direction (`agent_view = 1`). All other parameter values are set to GMSE defaults.

@@

**res_birth_type**: Resources in GMSE can be added to the model in one of two ways within the default resource sub-model, thereby simulating resource birth. It is important to note that `res_birth_type` refers only to additions that occur within the resource sub-model; additions from user actions (e.g., the `help_offspring` option) occurs within the user sub-model.

  0. *No explicit resource addition*. This option does not cause any baseline resource additions, but resource birth is still possible if `consume_repr > 0`. Under such conditions, landscape yield consumed by the resource will result in `floor(yield_consumed / consume_repr)` offspring produced. The amount of yield a resource consumes will be affected by both `times_feeding` (how many times the resource moves and feeds on a new landscape cell during a time step) and `res_consume` (the proportion of yield on a cell that is is consumed upon visit to the cell). Note that `consume_repr` can still be used when `res_birth_type > 0` (below), resulting in multiple sources of resource addition.
  1. *Fixed number added per resource*. For this option, each resource produces `lambda` new resources in each time step.
  2. *Poisson sampling*. For this option, each resource produces a number of offspring sampled independently from a Poisson distribution in which `lambda` is the rate parameter (i.e., each resource is expected to produce `lambda` offspring).

@@

  0. *No explicit density independent or dependent removal*. This option does not cause removal to be *directly* caused in a density independent or dependent way. Nevertheless, removal may still be possible if the argument `consume_surv > 0` (its default value is 0). In this case, survival of a resource in a time step depends on that resource consuming at least `consume_surv` in yield on the landscape. In such cases, a natural carrying capacity will be generated as more resources result in higher total consumption. The amount yield that a resource consumes is further affected by both `times_feeding` (how many times the resource moves and feeds on a new landscape cell during a time step) and `res_consume` (the proportion of yield on a cell that is is consumed upon visit to the cell). Note that `consume_surv` is can still be used when `res_death_type > 0` (below), resulting in multiple potential sources of removal.
  1. *Density-independent removal*. Given this option, there is no density-dependent removal of resources within the resource sub-model. Resources are simply removed with a probability of `removal_pr` each time the sub-model is run. This option should be used with great care because in the absence of density-dependence, it is possible for the population of resources to increase without limit and thereby greatly slow down simulation times. 
  2. *Density-dependent removal* (default). Given this option, removal of resources within the resource sub-model is caused entirely by density effects. The probability that a resource is removed is a function of the resource carrying capacity set using the `res_death_K` parameter. If the number of resources ($N$) is greater than `res_death_K` ($K$), then the probability that an individual resource is removed is defined by $(N - K) / N$. Removal then occurs independently for each resource based on this probability.
  3. *Density-independent and density-dependent removal*. This option allows a combination of both options (1) and (2), which affect removal independently. In other words, each resource is assigned a probability of removal `removal_pr` as in (1), and then independently assigned another probability of removal based on `res_death_K` as in (2). If removal occurs as a consequence of (1), (2), or both, then the resource is removed.

**observe_type**: Observation of resources in default GMSE v0.4.0.7 sub-models can occur in one of four ways. Each observation type mimics some process of resource observation, with potential error affected by observation intensity.

>>>>

|  public_land    |  0      | Pr. of land that is public (un-owned by users) if land_ownership = TRUE                          |
|  age_repr       |  1      | Age below which resources are incapable of reproducing                                           |
|  action_thres   |  0      | Pr. Deviation of the estimated population from the manager target, above which policy is updated |
|  budget_bonus   |  0      | Percentage of increase in budget a manager accrues by not updating policy in a time step         |
|  consume_surv   |  0      | Amount of yield a resource need to consume in a timestep to survive                              |
|  consume_repr   |  0      | Amount of yield a resource need to consume in a timestep to produce one offspring                |
|  times_feeding  |  1      | Number of searches that resources are allowed per time step for feeding on the landscape         |

@@

The code below calls `gmse` using the empirically derived parameters for Taiga Bean Geese described above. We also set `manager_budget = 10000` and `user_budget = 10000`. Further, we consider the case of a region in which farmland makes up 60% of all land, with 40% of land being 'public' (`public_land = 0.4`; which might be interpreted as any land in which stakeholders are not, or cannot be, invested in goose presence), and divide the farmland amongst 80 individual farmers (`stakeholders = 80`; `land_ownership = TRUE`). Landscape size is set to default 100 by 100 cells, so each farmer owns about 75 cells, which might be interpreted as hectares of land (for instructions on how to more precisely control landscape ownership, see the [advanced GMSE options](SI4.pdf) using `gmse_apply`). Because we need both density-dependent (`res_death_K = 93870`) and density-independent (`remove_pr = 0.122`) sources of mortality, we set `res_death_type = 3`. We assume that a single goose decreases agricultural production on a cell by 2% per time step (`res_consume = 0.02`). We further assume that the population is very well-monitored, with observers counting goose numbers on each cell of the landscape in every timestep (`observe_type = 3`) with the ability to observe one landscape cell in every direction (`agent_view = 1`). All other parameter values are set to GMSE defaults.

@@

**res_birth_type**: Resources in GMSE can be added to the model in one of two ways within the default resource sub-model, thereby simulating resource birth. It is important to note that `res_birth_type` refers only to additions that occur within the resource sub-model; additions from user actions (e.g., the `help_offspring` option) occur within the user sub-model.

  0. *No explicit resource addition*. This option causes no baseline resource additions, but resource birth is still possible if `consume_repr > 0`. Under such conditions, landscape yield consumed by the resource will result in `floor(yield_consumed / consume_repr)` offspring produced. The amount of yield a resource consumes will be affected by both `times_feeding` (how many times the resource moves and feeds on a new landscape cell during a time step) and `res_consume` (the proportion of yield on a cell that is consumed upon visit to the cell). Note that `consume_repr` can still be used when `res_birth_type > 0` (below), resulting in multiple sources of resource addition.
  1. *Fixed number added per resource*. For this option, each resource produces `lambda` new resources in each time step.
  2. *Poisson sampling*. For this option, each resource produces a number of offspring as determined by sampling from a Poisson distribution in which `lambda` is the rate parameter (i.e., each resource is expected to produce `lambda` offspring).

@@

  0. *No explicit density independent or dependent removal*. This option does not cause removal to be *directly* caused in a density independent or dependent way. Nevertheless, removal may still be possible if the argument `consume_surv > 0` (its default value is 0). In this case, survival of a resource in a time step depends on that resource consuming at least `consume_surv` in yield on the landscape. In such cases, a natural carrying capacity will be generated as more resources result in higher total consumption. The amount yield that a resource consumes is further affected by both `times_feeding` (how many times the resource moves and feeds on a new landscape cell during a time step) and `res_consume` (the proportion of yield on a cell that is is consumed upon visit to the cell). Note that `consume_surv` is can still be used when `res_death_type > 0` (below), resulting in multiple potential sources of removal. Given `res_death_type = 0`, **user actions have no effect** on resource removal (to ensure that user actions do have an effect, set `res_death_type = 1` and `removal_pr = 0`; see below).
  1. *Density-independent removal*. Given this option, there is no density-dependent removal of resources within the resource sub-model. Resources are simply removed with a fixed probability of `removal_pr` (its default value is 0) each time the sub-model is run. This option should be used with great care because in the absence of density-dependence, it is possible for the population of resources to increase without limit and thereby greatly slow down simulation times. 
  2. *Density-dependent removal* (default). Given this option, removal of resources within the resource sub-model is caused entirely by density effects. The probability that a resource is removed is a function of the resource carrying capacity set using the `res_death_K` parameter. If the number of resources ($N$) is greater than `res_death_K` ($K$), then the probability that an individual resource is removed is defined by $(N - K) / N$. Removal then occurs independently for each resource based on this probability.
  3. *Density-independent and density-dependent removal*. This option allows a combination of both options (1) and (2), which affect removal independently. In other words, each resource is assigned a probability of removal `removal_pr` as in (1), and then independently assigned another probability of removal based on `res_death_K` as in (2). If removal occurs as a consequence of (1), (2), or both, then the resource is removed.

**observe_type**: Observation of resources in default GMSE sub-models can occur in one of four ways. Each observation type mimics some process of resource observation, with potential error affected by observation intensity.
